\documentclass[a4paper,12pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[margin=3cm]{geometry}
\usepackage{times}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{subcaption}
\usepackage{mathtools}

\usepackage{lineno}
\linenumbers
\renewcommand{\baselinestretch}{1.5}
\usepackage{authblk}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\newcommand{\boldnabla}{\mbox{\boldmath$\nabla$}} % to be used in mathmode
\newcommand{\cbar}{\overline{\mathbb{C}}}% to be used in mathmode
\newcommand{\diff}[2]{\frac{d #1}{d #2}}% to be used in mathmode
\newcommand{\difff}[2]{\frac{d^2 #1}{d #2^2}}% to be used in mathmode
\newcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}} % to be used in mathmode
\newcommand{\pdifff}[2]{\frac{\partial^2 #1}{\partial #2^2}}% to be used in mathmode
\newcommand{\upperth}{$^{\mbox{\footnotesize{th}}}$}%to be used in text mode
\newcommand{\vect}[1]{\mathbf{#1}}% to be used in mathmode
\newcommand{\curl}[1]{\boldnabla \times \vect{#1}} % to be used in mathmode
\newcommand{\divr}[1]{\boldnabla \cdot \vect{#1}} %to be used in mathmode
\newcommand{\modu}[1]{\left| #1 \right|} %to be used in mathmode
\newcommand{\brak}[1]{\left( #1 \right)} % to be used in mathmode
\newcommand{\comm}[2]{\left[ #1 , #2 \right]} %to be used in mathmode
\newcommand{\dop}{\vect{d}} %to be used in mathmode
\newcommand{\cov}{\text{cov}} %to be used in mathmode
\newcommand{\var}{\text{var}} %to be used in mathmode
\newcommand{\mb}{\mathbf} %to be used in mathmode
\newcommand{\bs}{\boldsymbol} %to be used in mathmode
% Title Page
\title{A simple two parameter distribution for modelling neuronal activity and capturing neuronal association}
\date{}

\author[1]{Thomas Delaney}
\author[1]{Cian O'Donnell}
\affil[1]{School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, University of Bristol, Bristol, United Kingdom.}
\renewcommand\Affilfont{\itshape\small}

\begin{document}

\maketitle

%\tableofcontents

\abstract{Recent developments in electrophysiological technology have lead to an increase in the size of electrophysiological datasets. Consequently, there is a requirement for new analysis techniques that can make use of these new datasets, while remaining easy to use in practice. In this work, we fit the Conway-Maxwell-binomial distribution to spiking data read from a mouse exposed to visual stimuli.}

\section{Introduction}
  Motivate by pointing out how much computational power it can require to calculate $n$th order correlations.

  Point out that we don't necessarily need to measure correlations anyway.

\section{Results}

\section{Discussion}

\section{Data}

Details from data cortex lab here.

  \subsection{Experimental protocol}

\section{Methods}
Details about all kinds of things here.
    \subsection{Binning data}
    We converted the spike times for each cell into spike counts by putting the spike times into time bins of a given `width' (in seconds). We used time bins of $1$ms, $5$ms, and $10$ms. We used different time bin widths to assess the impact of choosing a bin width. 


    \subsection{Number of \textit{active} neurons}
    To count the number of active neurons in each neuronal ensemble, we split the time interval for each trial into bins of a given width. We counted the number of spikes fired by each cell in each bin. If a cell fired \textit{at least} one spike in a given bin, we regarded that cell as active in that bin. We recorded the number of active cells in every bin, and we recorded each cell's individual spike counts.
    
    It should be noted that when we used a bin width of $1$ms, the maximum number of spikes in any bin was $1$. For the wider time bins, some bins had spike counts greater than $1$. Consequently when using a bin width of $1$ms, the number of active neurons and the total spike count of a given bin were identical. But for wider bin widths, the total spike count was greater than the number of active neurons. 

    So for the $1$ms bin width, the activity of a neuron and the number of spikes fired by that neuron in any bin can be modelled as a Bernoulli variable. But for wider time bins, only the activity can be modelled in this way.

    \subsection{Moving windows for measurements}

    When taking measurements (e.g. moving average over the number of active neurons) or fitting distributions (eg. the beta binomial distribution) we slid a window containing a certain number of bins across the data, and made our measurements at each window position. For example, when analysing $1$ms bin data, we used a window containing $100$ bins, and we slid the window across the time interval for each trial moving $10$ bins at a time. So that for $2560$ms of data, we made $246$ measurements.

    For the $5$ms bin width data, we used windows containing $40$ bins, and slid the window $2$ bins at a time when taking measurements.

    For the $10$ms bin width data, we used windows containing $40$ bins, and slid the window $1$ bin at a time when taking measurements.
    
    By continuing to use windows containing $40$ bins, we retained statistical power but sacrificed the number of measurements taken. 

    \subsection{Fano factor}

    \subsection{Probability Distributions suitable for modelling ensemble activty}

      \subsubsection{Binomial distribution}

      \subsubsection{Beta-binomial distribution}

      \subsubsection{Conway-Maxwell-binomial distribution}

    \subsection{Goodness-of-fit}

    \subsection{Spike count correlations}

\section{Discussion}
Point out that the Conway-Maxwell-binomial distribution could be used to measure activity and association without having to sort the voltage traces into spikes. That does defeat the purpose slightly, however. 

\newpage
\bibliography{conway_maxwell_hierarchical_model.bbl}

\end{document}
